---
title: "SimCRC Slide Template"
subtitle: "Reusable Slides"
author: "SimCRC team"
format:
  revealjs:
    theme: default
    css: simcrc.css
    slide-number: true
    progress: false
    logo: simcrc-logo.png
    transition: fade
    incremental: true
    chalkboard:
      storage: null
      toggleChalkboardButton:
        left: "550px"
        bottom: "300px"
      toggleNotesButton:
        left: "550px"
        bottom: "300px"   
    include-after-body: sidebar.html
    code-copy: true
    code-overflow: wrap
    fig-width: 6
    fig-height: 4
    navigation-mode: linear
    controls-layout: edges
    font-size: 10px
execute:
  echo: true
  warning: false
  message: false
lang: en
# Uncomment and point to your BibTeX file if you want automatic references
bibliography: refs.bib
link-citations: true
# If you want your JS sidebar / progress behavior, uncomment the next line
 # include-after-body:
 #   - uw.js
---

## How to use this template library

-   This file is a **library of slide examples**\
-   We can copy–paste any slide we like into our actual presentation `.qmd`
-   All slides use the **UW theme** from `uw.css`
-   We can safely delete sections we don’t need
-   This delimiter `-----------` is used to separate slides although is not necessary

::: footer
 Several Quarto examples published in their tutorial were used in this library: [Fragments](https://quarto.org/docs/presentations/revealjs/advanced.html)
:::


------------------------------------------------------------------------

## Example slide for incremntal bullet points

By the end of this section, participants should be able to:

::: incremental
-   Explain the intuition behind **\[method / concept\]**
-   Describe the key assumptions required for valid inference
-   Implement a simple example in R and interpret the output
-   Discuss when this method is appropriate in **HEOR**
:::

------------------------------------------------------------------------

## Example of Key definition / concept slide

We can use this for central definitions like ICER, odds ratio, etc.

::: callout-note
## Definition: Incremental Cost-Effectiveness Ratio (ICER) {.small-text}

The ICER compares two strategies, 1 and 0:

$$
\text{ICER} = \frac{C_1 - C_0}{E_1 - E_0}
$$

where $C$ is **cost** and $E$ is **effectiveness** (e.g., QALYs).
:::

::: incremental
-   If the **denominator is small**, ICERs can be unstable\
-   We often complement ICERs with **Net Monetary Benefit (NMB)**
-   Choice of **WTP threshold** is crucial for interpretation
:::

------------------------------------------------------------------------

## Worked example / derivation

We can reveal derivation steps gradually.

We want to estimate the effect of $X$ on $Y$:

$$
Y_i = \beta_0 + \beta_1 X_i + \varepsilon_i
$$

::: incremental
1.  Assume $\mathbb{E}[\varepsilon_i \mid X_i] = 0$
2.  Use **least squares** to choose $\hat{\beta}_0, \hat{\beta}_1$
3.  The slope estimator can be written as: $$
    \hat{\beta}_1 = 
    \frac{\sum_i (X_i - \bar{X})(Y_i - \bar{Y})}
    {\sum_i (X_i - \bar{X})^2}
    $$
4.  Interpretation (HEOR):\
    “A one-unit increase in $X$ is associated with an average change of $\hat{\beta}_1$ units in $Y$, under the model assumptions.”
:::

------------------------------------------------------------------------

## Example of quick quiz 

**Question**

A logistic regression model estimates the log-odds of screening uptake.\
Which of the following is *not* an appropriate interpretation?

::: incremental
-   A. The exponentiated coefficient gives an **odds ratio**
-   B. The model assumes a **logit link** between predictors and probabilities
-   C. The linear predictor can be interpreted as a **risk difference**
-   D. We can obtain predicted **probabilities** from the model

-   **Answer:**\
-   The incorrect statement is **C** (the linear predictor is on the log-odds scale, not a risk difference).
:::

------------------------------------------------------------------------

## Activity / discussion slide

::: incremental
1.  In your own work, what **binary outcomes** could be modeled with logistic regression?
2.  Which **assumptions** would you worry about (e.g., linearity in the logit, independence)?
3.  How would you **communicate** model results to a non-technical policymaker?

> Be ready to share **one concrete example** from your discussion.
:::

------------------------------------------------------------------------

## Fragments (1)

Incremental text display and animation with fragments:

<br/>

::: {.fragment .fade-in}
Fade in
:::

::: {.fragment .fade-up}
Slide up while fading in
:::

::: {.fragment .fade-left}
Slide left while fading in
:::

::: {.fragment .fade-in-then-semi-out}
Fade in then semi out
:::


::: footer
Learn more: [Fragments](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/advanced.html#fragments)
:::

------------------------------------------------------------------------

## Fragments (2)

Incremental text display and animation with fragments:

<br/>


::: {.fragment .strike}
Strike
:::

::: {.fragment .highlight-red}
Highlight red
:::

::: {.fragment .custom .blur}
First item to be unblurred
:::

::: {.fragment .custom .blur}
Second one to be revealed
:::


::: footer
Learn more: [Fragments](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/advanced.html#fragments)
:::

------------------------------------------------------------------------

## Code + output (R example) {.medium-text .small-table}

Example: logistic regression for CRC screening uptake.

```{r}
#| echo: true
#| message: false
#| warning: false

library(dplyr)
library(pander)

set.seed(123)
n <- 200

dat <- tibble(
  age      = rnorm(n, mean = 55, sd = 7),
  insured  = rbinom(n, 1, 0.7),
  screened = rbinom(n, 1, plogis(-5 + 0.06 * age + 0.8 * insured))
)

fit <- glm(screened ~ age + insured,
           data = dat,
           family = binomial)

pander(summary(fit),
       caption = "Logistic regression results for CRC screening uptake",
       digits = 3,
       split.table = 80,
       style = "rmarkdown",
       missing = "NA")


```

::: incremental
-   `age` has a **positive association** with screening probability\
-   Being **insured** increases the odds of screening\
-   Coefficients can be exponentiated to get **odds ratios**
:::

------------------------------------------------------------------------

## Code Animations {auto-animate="true"}

-   Over 20 syntax highlighting themes available
-   Default theme optimized for accessibility

``` r
# Define a server for the Shiny app
function(input, output) {
  
  # Fill in the spot we created for a plot
  output$phonePlot <- renderPlot({
    # Render a barplot
    barplot(WorldPhones[,input$region]*1000, 
            main=input$region,
            ylab="Number of Telephones",
            xlab="Year")
  })
}
```

::: footer
Learn more: [Code Animations](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/advanced.html#code-animations)
:::

## Line Highlighting

-   Highlight specific lines for emphasis
-   Incrementally highlight additional lines

``` {.python code-line-numbers="4-5|7|10"}
import numpy as np
import matplotlib.pyplot as plt

r = np.arange(0, 2, 0.01)
theta = 2 * np.pi * r
fig, ax = plt.subplots(subplot_kw={'projection': 'polar'})
ax.plot(theta, r)
ax.set_rticks([0.5, 1, 1.5, 2])
ax.grid(True)
plt.show()
```

::: footer
Learn more: [Line Highlighting](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/#line-highlighting)
:::

------------------------------------------------------------------------

## Executable Code

```{r}
#| echo: true
#| fig-width: 10
#| fig-height: 4.5
library(ggplot2)
ggplot(mtcars, aes(hp, mpg, color = am)) +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess")
```

::: footer
Learn more: [Executable Code](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/#executable-code)
:::

------------------------------------------------------------------------

## LaTeX Equations

[MathJax](https://www.mathjax.org/) rendering of equations to HTML

::: columns
::: {.column width="40%"}
``` tex
\begin{gather*}
a_1=b_1+c_1\\
a_2=b_2+c_2-d_2+e_2
\end{gather*}

\begin{align}
a_{11}& =b_{11}&
  a_{12}& =b_{12}\\
a_{21}& =b_{21}&
  a_{22}& =b_{22}+c_{22}
\end{align}
```
:::

::: {.column width="60%"}
```{=tex}
\begin{gather*}
a_1=b_1+c_1\\
a_2=b_2+c_2-d_2+e_2
\end{gather*}
```
```{=tex}
\begin{align}
a_{11}& =b_{11}&
  a_{12}& =b_{12}\\
a_{21}& =b_{21}&
  a_{22}& =b_{22}+c_{22}
\end{align}
```
:::
:::

::: footer
Learn more: [LaTeX Equations](https://{{< meta prerelease-subdomain >}}quarto.org/docs/authoring/markdown-basics.html#equations)
:::

------------------------------------------------------------------------

## Column Layout {.smaller}

Arrange content into columns of varying widths:

::: columns
::: {.column width="35%"}
#### Motor Trend Car Road Tests

The data was extracted from the 1974 Motor Trend US magazine, and comprises fuel consumption and 10 aspects of automobile design and performance for 32 automobiles.
:::

::: {.column width="3%"}
:::

::: {.column width="62%"}
```{r}
#| echo: false
knitr::kable(head(mtcars)[,c("mpg",	"cyl", "disp", "hp", "wt")])
```
:::
:::

::: footer
Learn more: [Multiple Columns](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/#multiple-columns)
:::

------------------------------------------------------------------------

## Slide Backgrounds {background="#43464B"}

Set the `background` attribute on a slide to change the background color (all CSS color formats are supported).

Different background transitions are available via the `background-transition` option.

::: footer
Learn more: [Slide Backgrounds](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/#color-backgrounds)
:::

------------------------------------------------------------------------

## Auto-Animate {auto-animate="true" auto-animate-easing="ease-in-out"}

Automatically animate matching elements across slides with Auto-Animate.

::: r-hstack
::: {data-id="box1" auto-animate-delay="0" style="background: #2780e3; width: 200px; height: 150px; margin: 10px;"}
:::

::: {data-id="box2" auto-animate-delay="0.1" style="background: #3fb618; width: 200px; height: 150px; margin: 10px;"}
:::

::: {data-id="box3" auto-animate-delay="0.2" style="background: #e83e8c; width: 200px; height: 150px; margin: 10px;"}
:::
:::

::: footer
Learn more: [Auto-Animate](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/advanced.html#auto-animate)
:::

## Auto-Animate {auto-animate="true" auto-animate-easing="ease-in-out"}

Automatically animate matching elements across slides with Auto-Animate.

::: r-stack
::: {data-id="box1" style="background: #2780e3; width: 350px; height: 350px; border-radius: 200px;"}
:::

::: {data-id="box2" style="background: #3fb618; width: 250px; height: 250px; border-radius: 200px;"}
:::

::: {data-id="box3" style="background: #e83e8c; width: 150px; height: 150px; border-radius: 200px;"}
:::
:::

::: footer
Learn more: [Auto-Animate](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/advanced.html#auto-animate)
:::
------------------------------------------------------------------------

## Tabsets {.smaller .scrollable transition="slide"}

::: panel-tabset
### Plot

```{r}
library(ggplot2)
ggplot(mtcars, aes(hp, mpg, color = am)) +
  geom_point() +
  geom_smooth(formula = y ~ x, method = "loess")
```

### Data

```{r}
knitr::kable(mtcars)
```
:::

::: footer
Learn more: [Tabsets](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/#tabsets)
:::

## Interactive Slides {.smaller transition="slide"}

Include Jupyter widgets and htmlwidgets in your presentations

```{r}
#| echo: false
#| fig-height: 5
library(leaflet)
leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lng=174.768, lat=-36.852, popup="The birthplace of R")
```

::: footer
Learn more: [Jupyter widgets](https://{{< meta prerelease-subdomain >}}quarto.org/docs/interactive/widgets/jupyter.html), [htmlwidgets](https://{{< meta prerelease-subdomain >}}quarto.org/docs/interactive/widgets/htmlwidgets.html)
:::

------------------------------------------------------------------------

## Table slide with smaller font {.small-table}

```{r}
#| echo: false
#| tbl-cap: "Baseline characteristics (demo)"
#| class: small
library(dplyr)
library(gt)
library(pander)

tab_example <- dat |>
  summarize(
    n          = n(),
    mean_age   = mean(age),
    sd_age     = sd(age),
    prop_ins   = mean(insured),
    prop_scr   = mean(screened)
  )
# Display the table with markdown formatting with font size 24

pander(tab_example,
       caption = "Baseline characteristics (demo)",
       digits = 2)


```

> Tip: the `class: small-table` option shrinks the font size for dense tables.

------------------------------------------------------------------------

## Chalkboard {chalkboard-buttons="true"}

::: {style="margin-bottom: 1.9em;"}
Free form drawing and slide annotations
:::

Use the chalkboard button at the bottom left of the slide to toggle the chalkboard.

Use the notes canvas button at the bottom left of the slide to toggle drawing on top of the current slide.

You can also press {{< kbd b >}} to toggle the chalkboard or {{< kbd c >}} to toggle the notes canvas.

::: footer
Learn more: [Chalkboard](https://{{< meta prerelease-subdomain >}}quarto.org/docs/presentations/revealjs/presenting.html#chalkboard)
:::

------------------------------------------------------------------------


## Interactive tabset (multiple tables)

```{r}
#| echo: false
# Create a simple model results table
library(broom)

model_tab <- tidy(fit) |>
  select(term, estimate, std.error, statistic, p.value)
```

::: panel-tabset
### Baseline characteristics

```{r}
#| echo: false
#| class: small
library(gt)
 
 gt(tab_example) |>
  fmt_number(
    columns = everything(),
    decimals = 2
  ) |>
  tab_header(
    title = "Baseline characteristics"
  )
```

### Model estimates

```{r}
#| echo: false
#| class: small

gt(model_tab,
   rowname_col = "term") |>
  fmt_number(
    columns = c(estimate, std.error, statistic, p.value),
    decimals = 3
  ) |>
  tab_header(
    title = "Logistic regression model estimates"
  )
```
:::

------------------------------------------------------------------------

## Interactive plot (plotly scatter)

```{r}
#| echo: false
#| fig-height: 4

library(plotly)

p <- plot_ly(
  data = dat,
  x    = ~age,
  y    = ~screened,
  type = "scatter",
  mode = "markers",
  color = ~factor(insured),
  text  = ~paste("Age:", round(age,1),
                 "<br>Insured:", insured,
                 "<br>Screened:", screened)
) |>
  layout(
    title = "Interactive scatter: screening vs age",
    xaxis = list(title = "Age"),
    yaxis = list(title = "Screened (0/1)")
  )

p
```


------------------------------------------------------------------------

## Dynamic Simulation Plot – 10 Random Walks

This slide shows 10 independent random walks. Each line is a trajectory, and the animation reveals them step by step.

```{r}
#| echo: false
#| fig-height: 5
#| font-size: 10

library(plotly)

set.seed(123)

n_walks <- 10
n_steps <- 50
steps   <- 1:n_steps

# Generate 10 random walks
rw_list <- lapply(1:n_walks, function(w) {
  increments <- rnorm(n_steps, mean = 0, sd = 0.4)
  y          <- cumsum(increments)
  data.frame(
    walk = paste0("Walk ", w),
    step = steps,
    y    = y
  )
})

rw_df <- do.call(rbind, rw_list)

# Build cumulative frames so each frame shows the full path up to that step
frames_list <- lapply(steps, function(f) {
  tmp <- subset(rw_df, step <= f)
  tmp$frame <- f
  tmp
})

anim_df <- do.call(rbind, frames_list)

# Plotly animated random walks
p_dyn <- plot_ly(
  data  = anim_df,
  x     = ~step,
  y     = ~y,
  color = ~walk,
  frame = ~frame,
  type  = "scatter",
  mode  = "lines",
  line  = list(width = 2)
) |>
  layout(
    title  = "Animated Random Walks (10 trajectories)",
    xaxis  = list(title = "Step"),
    yaxis  = list(title = "Value"),
    legend = list(orientation = "v", x = 50, y = 0)
  )

p_dyn

```

------------------------------------------------------------------------

## Microsimulation vs DES – Loop Iterations



::: columns
::: {.column width="35%"}
This animation focuses on **how many loop iterations** each approach needs to reach the absorbing state (**Dead**) over a 30-year horizon.
:::

::: {.column width="3%"}
:::

::: {.column width="62%"}
```{r}
#| echo: false
#| fig-height: 5

library(plotly)
library(dplyr)

# ---------------------------------------------------------
# 1. Setup: health states and event times
# ---------------------------------------------------------
states <- c("Healthy", "Mild", "Moderate", "Severe", "Dead")

# "True" continuous-time event times (in years) for this individual
# H -> Mild -> Moderate -> Severe -> Dead
event_times <- c(4.3, 9.7, 13.2, 17.0)
t_horizon   <- 30
max_iter    <- 30   # loop iterations 0..30

# Helper: state index at a given *time* t
state_at_time <- function(t) {
  if (t <  event_times[1]) return(1)  # Healthy
  if (t <  event_times[2]) return(2)  # Mild
  if (t <  event_times[3]) return(3)  # Moderate
  if (t <  event_times[4]) return(4)  # Severe
  return(5)                           # Dead
}

# ---------------------------------------------------------
# 2. Microsimulation: loop over all years 0..30
# ---------------------------------------------------------
micro_steps  <- 0:max_iter
micro_time   <- micro_steps            # 1 step = 1 year
micro_state  <- sapply(micro_time, state_at_time)

micro_df <- data.frame(
  step   = micro_steps,
  time   = micro_time,
  state  = micro_state,
  method = "Microsim (1-year cycles)"
)

# ---------------------------------------------------------
# 3. DES: loop only over events
#    Each iteration jumps directly to the next event time
# ---------------------------------------------------------
# Step 0: time 0, Healthy
des_step_idx  <- 0:length(event_times)    # 0,1,2,3,4
des_time      <- c(0, event_times)       # time reached at each DES iteration
des_state_idx <- sapply(des_time, state_at_time)

des_core <- data.frame(
  step   = des_step_idx,
  time   = des_time,
  state  = des_state_idx,
  method = "DES (event-driven)"
)

# ---------------------------------------------------------
# 4. Build frames: for each overall loop iteration f = 0..30
#    - Microsim has evaluated f steps.
#    - DES has evaluated up to min(f, last DES step).
# ---------------------------------------------------------
make_frame <- function(f) {
  # Microsim: show path up to current loop iteration f
  micro_part <- micro_df %>%
    filter(step <= f)
  
  # DES: it only has steps 0..max(des_step_idx);
  # after that, we just keep showing the same completed path.
  max_des_step <- max(des_core$step)
  des_part <- des_core %>%
    filter(step <= min(f, max_des_step))
  
  df <- bind_rows(micro_part, des_part)
  df$frame <- f
  df
}

frames_list <- lapply(0:max_iter, make_frame)
anim_df <- bind_rows(frames_list)

# ---------------------------------------------------------
# 5. Plotly animated step plot: state vs loop iteration
# ---------------------------------------------------------
p_iter <- plot_ly(
  data  = anim_df,
  x     = ~time,
  y     = ~state,
  frame = ~frame,
  color = ~method,
  type  = "scatter",
  mode  = "lines+markers",
  line  = list(shape = "hv", width = 3),
  marker = list(size = 8)
) %>%
  layout(
    title = "Microsimulation vs DES – Health State by Loop Iteration",
    xaxis = list(
      title = "Loop iteration",
      range = c(0, max_iter)
    ),
    yaxis = list(
      title    = "Health state",
      tickmode = "array",
      tickvals = 1:5,
      ticktext = states,
      range    = c(0.5, 5.5)
    ),
    legend = list(orientation = "h", x = 0.05, y = -0.15),
    margin = list(b = 80)
  )

p_iter

```
:::
:::

------------------------------------------------------------------------

## Dynamic PSA CE-Plane “Movie”

This slide shows a dynamic cost-effectiveness (CE) plane.  
Each frame reveals a new batch of PSA draws for incremental cost vs. incremental QALYs.

```{r}
#| echo: false
#| fig-height: 5

library(plotly)

set.seed(123)

# Simulate simple PSA results
n_psa  <- 200
lambda <- 50000   # WTP per QALY (for reference line, if wanted)

psa_df <- data.frame(
  id         = 1:n_psa,
  delta_qaly = rnorm(n_psa, mean = 0.05, sd = 0.03),
  delta_cost = rnorm(n_psa, mean = 1000, sd = 600)
)

# Create "batches" of points to show in each frame
batch_size <- 20
psa_df$batch <- ceiling(psa_df$id / batch_size)

p_ce <- plot_ly(
  data  = psa_df,
  x     = ~delta_qaly,
  y     = ~delta_cost,
  frame = ~batch,
  type  = "scatter",
  mode  = "markers",
  marker = list(
    size  = 9,
    color = "#4B2E83",
    line  = list(width = 1, color = "#B7A57A")
  ),
  text = ~paste0(
    "Draw #: ", id,
    "<br>ΔQALY: ", round(delta_qaly, 3),
    "<br>ΔCost: $", round(delta_cost, 0)
  ),
  hoverinfo = "text"
) |>
  layout(
    title = "Dynamic CE-Plane: PSA Draws Over Time",
    xaxis = list(title = "ΔQALYs", zeroline = TRUE),
    yaxis = list(title = "ΔCost (USD)", zeroline = TRUE),
    margin = list(l = 60, r = 40, b = 70, t = 60)
  )

p_ce

```

------------------------------------------------------------------------

## Process Diagram (Animated)

This example shows a simple modeling workflow. Each step will appear one by one
as you advance through the slide.

::: {.process-row}

::: {.process-step .fragment}
#### 1. Define Question
Clarify population, intervention, comparator, outcomes, and time horizon.
:::

::: {.process-step .fragment}
#### 2. Collect Data
Assemble data on epidemiology, costs, and health outcomes from valid sources.
:::

::: {.process-step .fragment}
#### 3. Build Model
Choose structure (e.g., decision tree, Markov, DES) and parameter inputs.
:::

::: {.process-step .fragment}
#### 4. Analyze & Communicate
Run scenarios, perform sensitivity analyses, and present clear recommendations.
:::

:::

------------------------------------------------------------------------

## Process Diagram (Horizontal Pipeline)

This version shows a left-to-right workflow with arrows between steps.  
Each step appears as you advance through the slide.

::: {.pipeline-row}

::: {.pipeline-step .fragment}
#### 1. Define Question
Clarify population, intervention, comparator, outcomes, and time horizon.
:::

::: {.pipeline-step .fragment}
#### 2. Collect Data
Assemble data on epidemiology, costs, and health outcomes from valid sources.
:::

::: {.pipeline-step .fragment}
#### 3. Build Model
Choose structure (e.g., decision tree, Markov, DES) and parameter inputs.
:::

::: {.pipeline-step .fragment}
#### 4. Analyze & Communicate
Run scenarios, perform sensitivity analyses, and present clear recommendations.
:::

:::

------------------------------------------------------------------------

## Embedding a Shiny app via iframe

::: panel-tabset
### Statistical distirbutions

```{=html}
<iframe
  src="https://cpineda.shinyapps.io/statistical_distribution/"
  width="100%"
  height="450"
  style="border: none;"
>
</iframe>
```
### RR vs HR vs OR

```{=html}
<iframe
  src="https://cpineda.shinyapps.io/App_RR_HR_OR/"
  width="100%"
  height="450"
  style="border: none;"
>
</iframe>
```
:::

-------------------------------------------------------------------------

## Embedding a web page via iframe


```{=html}
<iframe
  src="https://www.shinyapps.org/apps/RGraphCompendium/index.php#preface"
  width="100%"
  height="500"
  style="border: none;"
>
</iframe>
```


------------------------------------------------------------------------


## References (manual list)

Use this version if you don’t want BibTeX / citation keys.

-   Briggs A, Claxton K, Sculpher M. *Decision Modelling for Health Economic Evaluation.* Oxford University Press; 2006.\
-   Jansen JP, et al. Indirect treatment comparison / network meta-analysis… *Value Health.* 2014;17(2):157–173.\
-   Hunink MGM, et al. *Decision Making in Health and Medicine.* Cambridge University Press; 2014.

------------------------------------------------------------------------

## References with citation keys (if using BibTeX)

class: uw-ref-slide

If We want Quarto to build references automatically:

1.  Create a `refs.bib` file in the same folder\
2.  Add `bibliography: refs.bib` and `link-citations: true` to the YAML\
3.  Use citation keys like this in the text: @rubin1978, @heckman1979, etc.

Then add a slide with the references (next slide):

------------------------------------------------------------------------

## References

::: {#refs}
:::

------------------------------------------------------------------------
