---
title: "BayCANN Calibration summary"
author: "SimCRC team"
date: last-modified
format:
  html:
    toc: true
    toc-depth: 2
    number-sections: true
    fig-cap-location: bottom
  pdf:
    toc: true
    number-sections: true
execute:
  echo: false
  warning: false
  message: false
  error: false
---

```{r echo=FALSE, message=FALSE, warning=FALSE}

load("paths_calibration.RData")
load("calibration_setup.RData")

version <- paths_calibration$cal_version

lesion_type <- paths_calibration$Lesion_type

population <- paths_calibration$Population_type

date_cal <- paths_calibration$Date_version

BayCANN_version <- paths_calibration$BayCANN_version

#Read calibration description
calibration_description <- paste0("Calibration_description_", BayCANN_version, ".txt")
calibration_description_text <- readLines(calibration_description)

```

-   Model verson: `r version`
-   Lesion type: `r lesion_type`
-   Population: `r population`
-   Date of calibration: `r date_cal`
-   Calibration description:  `r calibration_description_text`


## LHS coverage analysis

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Show coverage analysis figures

fig_coverage_num <- paste0("fig_coverage_num_", BayCANN_version, ".png")
fig_coverage_cat <- paste0("fig_coverage_cat_", BayCANN_version, ".png")

plot_coverage_num <- png::readPNG(fig_coverage_num)
plot_coverage_cat <- png::readPNG(fig_coverage_cat)

#Plot the coverage analysis figures
library(grid)
grid::grid.newpage()
grid::grid.draw(rasterGrob(plot_coverage_num))
grid::grid.newpage()
grid::grid.draw(rasterGrob(plot_coverage_cat))


```

## Prediction performance of ANN

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Show prediction performance figures
fig_ANN_prediction_performance <- paste0("fig_ANN_prediction_performance_", BayCANN_version, ".png")
plot_ANN_performance <- png::readPNG(fig_ANN_prediction_performance)
#Plot the prediction performance figure
grid::grid.newpage()
grid::grid.draw(rasterGrob(plot_ANN_performance))
```

## Posterior chains distribution

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Show posterior distribution chains figure
fig_posterior_distribution_chains <- paste0("fig_posterior_distribution_chains_", BayCANN_version, ".png")
plot_posterior_chains <- png::readPNG(fig_posterior_distribution_chains)
#Plot the posterior distribution chains figure
grid::grid.newpage()
grid::grid.draw(rasterGrob(plot_posterior_chains))
```

## Prior versus Posterior distributions

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Show prior versus posterior distributions figure
fig_prior_vs_posterior <- paste0("fig_prior-vs-posterior_", BayCANN_version, ".png")
plot_prior_vs_posterior <- png::readPNG(fig_prior_vs_posterior)
#Plot the prior versus posterior distributions figure
grid::grid.newpage()
grid::grid.draw(rasterGrob(plot_prior_vs_posterior))
```

## Internal Validation

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Show internal validation figures
fig_internall_validation_ch_1_num <- paste0("fig_internall_validation_", BayCANN_version, "_num.png")
fig_internall_validation_ch_1_cat <- paste0("fig_internall_validation_", BayCANN_version, "_cat.png")
plot_internal_validation_num <- png::readPNG(fig_internall_validation_ch_1_num)
plot_internal_validation_cat <- png::readPNG(fig_internall_validation_ch_1_cat)
#Plot the internal validation figures
grid::grid.newpage()
grid::grid.draw(rasterGrob(plot_internal_validation_num))
grid::grid.newpage()
grid::grid.draw(rasterGrob(plot_internal_validation_cat))
```

## Parameter set validation

```{r echo=FALSE, message=FALSE, warning=FALSE}
#Show parameter set validation figures
fig_parameter_set_validation_num <- paste0("fig_parameter_set_validation_num_", BayCANN_version, ".png")
fig_parameter_set_validation_cat <- paste0("fig_parameter_set_validation_cat_", BayCANN_version, ".png")
plot_parameter_set_validation_num <- png::readPNG(fig_parameter_set_validation_num)
plot_parameter_set_validation_cat <- png::readPNG(fig_parameter_set_validation_cat)
#Plot the parameter set validation figures
grid::grid.newpage()
grid::grid.draw(rasterGrob(plot_parameter_set_validation_num))
grid::grid.newpage()
grid::grid.draw(rasterGrob(plot_parameter_set_validation_cat))
```

## Parameter summary table

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Load the best parameter set
l_params_calibrated_sets <- paste0("l_params_calibrated_sets_", BayCANN_version, ".RData")
load(l_params_calibrated_sets)

#Get the best parameter: Max likelihood
l_params_calibrated <- l_params_calibrated_sets$Max_log_likelihood

SSP_cal <- calibration_setup$SSP_pathway #TRUE if we want to include SSP pathway


if(SSP_cal){
 # Compare the parameters for adenoma and SSP

df_params_comparison <- data.frame(
  Parameter = c(
                "alpha_lesion",
                "beta_age",
                "AdNaturalHistoryPropensity_Gaussian_Variance",
                "AdGrowth_Exp_Rate_1_to_6_P",
                "AdGrowth_Exp_Rate_1_to_6_D",
                "AdGrowth_Exp_Rate_1_to_6_R",
                "AdGrowth_Exp_Rate_6_to_10_P",
                "AdGrowth_Exp_Rate_6_to_10_D",
                "AdGrowth_Exp_Rate_6_to_10_R",
                "CancerOnset_Gompertz_Shape_P",
                "CancerOnset_Gompertz_Shape_D",
                "CancerOnset_Gompertz_Shape_R",
                "CancerOnset_Gompertz_Rate_P",
                "CancerOnset_Gompertz_Rate_D",
                "CancerOnset_Gompertz_Rate_R",
                "PreclinCancerProg_Exp_Rate_S1S2_P",
                "PreclinCancerProg_Exp_Rate_S1S2_D",
                "PreclinCancerProg_Exp_Rate_S1S2_R",
                "PreclinCancerProg_Exp_Rate_S2S3_P",
                "PreclinCancerProg_Exp_Rate_S2S3_D",
                "PreclinCancerProg_Exp_Rate_S2S3_R",
                "PreclinCancerProg_Exp_Rate_S3S4_P",
                "PreclinCancerProg_Exp_Rate_S3S4_D",
                "PreclinCancerProg_Exp_Rate_S3S4_R"),

  Adenoma = c(l_params_calibrated$alpha_lesion_adenoma, 
              l_params_calibrated$beta_age,
              l_params_calibrated$AdNaturalHistoryPropensity_Gaussian_Variance,
              l_params_calibrated$AdGrowth_Exp_Rate_1_to_6_P,
              l_params_calibrated$AdGrowth_Exp_Rate_1_to_6_D,
              l_params_calibrated$AdGrowth_Exp_Rate_1_to_6_R,
              l_params_calibrated$AdGrowth_Exp_Rate_6_to_10_P,
              l_params_calibrated$AdGrowth_Exp_Rate_6_to_10_D,
              l_params_calibrated$AdGrowth_Exp_Rate_6_to_10_R,
              l_params_calibrated$CancerOnset_Gompertz_Shape_P,
              l_params_calibrated$CancerOnset_Gompertz_Shape_D,
              l_params_calibrated$CancerOnset_Gompertz_Shape_R,
              l_params_calibrated$CancerOnset_Gompertz_Rate_P,
              l_params_calibrated$CancerOnset_Gompertz_Rate_D,
              l_params_calibrated$CancerOnset_Gompertz_Rate_R,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S1S2_P,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S1S2_D,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S1S2_R,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S2S3_P,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S2S3_D,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S2S3_R,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S3S4_P,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S3S4_D,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S3S4_R),
  SSP = c(l_params_calibrated$alpha_lesion_ssp, 
          l_params_calibrated$beta_age_ssp,
          l_params_calibrated$AdNaturalHistoryPropensity_Gaussian_Variance,
          l_params_calibrated$AdGrowth_Exp_Rate_1_to_6_P*l_params_calibrated$hr_SSPGrowth_1_to_6_P,
          l_params_calibrated$AdGrowth_Exp_Rate_1_to_6_D*l_params_calibrated$hr_SSPGrowth_1_to_6_D,
          l_params_calibrated$AdGrowth_Exp_Rate_1_to_6_R*l_params_calibrated$hr_SSPGrowth_1_to_6_R,
          l_params_calibrated$AdGrowth_Exp_Rate_6_to_10_P*l_params_calibrated$hr_SSPGrowth_6_to_10_P,
          l_params_calibrated$AdGrowth_Exp_Rate_6_to_10_D*l_params_calibrated$hr_SSPGrowth_6_to_10_D,
          l_params_calibrated$AdGrowth_Exp_Rate_6_to_10_R*l_params_calibrated$hr_SSPGrowth_6_to_10_R,
          l_params_calibrated$CancerOnset_Gompertz_Shape_P,
          l_params_calibrated$CancerOnset_Gompertz_Shape_D,
          l_params_calibrated$CancerOnset_Gompertz_Shape_R,
          l_params_calibrated$CancerOnset_Gompertz_Rate_P*l_params_calibrated$hr_SSPCancerOnset_P,  #Change
          l_params_calibrated$CancerOnset_Gompertz_Rate_D*l_params_calibrated$hr_SSPCancerOnset_P,  #Change if lesion specific
          l_params_calibrated$CancerOnset_Gompertz_Rate_R*l_params_calibrated$hr_SSPCancerOnset_P,  #Change if lesion specific
          l_params_calibrated$PreclinCancerProg_Exp_Rate_S1S2_P,
          l_params_calibrated$PreclinCancerProg_Exp_Rate_S1S2_D,
          l_params_calibrated$PreclinCancerProg_Exp_Rate_S1S2_R,
          l_params_calibrated$PreclinCancerProg_Exp_Rate_S2S3_P,
          l_params_calibrated$PreclinCancerProg_Exp_Rate_S2S3_D,
          l_params_calibrated$PreclinCancerProg_Exp_Rate_S2S3_R,
          l_params_calibrated$PreclinCancerProg_Exp_Rate_S3S4_P,
          l_params_calibrated$PreclinCancerProg_Exp_Rate_S3S4_D,
          l_params_calibrated$PreclinCancerProg_Exp_Rate_S3S4_R)
)

#Get percentage difference between adenoma and SSP parameters
df_params_comparison$Percentage_Difference <- round(
  (df_params_comparison$SSP - df_params_comparison$Adenoma) / df_params_comparison$Adenoma * 100, 2
)

#Create a table to display the dataframe
library(knitr)
kable(df_params_comparison, 
      caption = "Comparison of parameters between Adenoma and SSP pathways",
      col.names = c("Parameter", "Adenoma", "SSP", "Percentage Difference (%)"),
      digits = 3,
      format = "html",align = "l")

} else {
 
# Get the parameters for adenoma pathway

df_params_comparison <- data.frame(
  Parameter = c(
                "alpha_lesion",
                "beta_age",
                "AdNaturalHistoryPropensity_Gaussian_Variance",
                "AdGrowth_Exp_Rate_1_to_6_P",
                "AdGrowth_Exp_Rate_1_to_6_D",
                "AdGrowth_Exp_Rate_1_to_6_R",
                "AdGrowth_Exp_Rate_6_to_10_P",
                "AdGrowth_Exp_Rate_6_to_10_D",
                "AdGrowth_Exp_Rate_6_to_10_R",
                "CancerOnset_Gompertz_Shape_P",
                "CancerOnset_Gompertz_Shape_D",
                "CancerOnset_Gompertz_Shape_R",
                "CancerOnset_Gompertz_Rate_P",
                "CancerOnset_Gompertz_Rate_D",
                "CancerOnset_Gompertz_Rate_R",
                "PreclinCancerProg_Exp_Rate_S1S2_P",
                "PreclinCancerProg_Exp_Rate_S1S2_D",
                "PreclinCancerProg_Exp_Rate_S1S2_R",
                "PreclinCancerProg_Exp_Rate_S2S3_P",
                "PreclinCancerProg_Exp_Rate_S2S3_D",
                "PreclinCancerProg_Exp_Rate_S2S3_R",
                "PreclinCancerProg_Exp_Rate_S3S4_P",
                "PreclinCancerProg_Exp_Rate_S3S4_D",
                "PreclinCancerProg_Exp_Rate_S3S4_R"),

  Adenoma = c(l_params_calibrated$alpha_lesion_adenoma, 
              l_params_calibrated$beta_age,
              l_params_calibrated$AdNaturalHistoryPropensity_Gaussian_Variance,
              l_params_calibrated$AdGrowth_Exp_Rate_1_to_6_P,
              l_params_calibrated$AdGrowth_Exp_Rate_1_to_6_D,
              l_params_calibrated$AdGrowth_Exp_Rate_1_to_6_R,
              l_params_calibrated$AdGrowth_Exp_Rate_6_to_10_P,
              l_params_calibrated$AdGrowth_Exp_Rate_6_to_10_D,
              l_params_calibrated$AdGrowth_Exp_Rate_6_to_10_R,
              l_params_calibrated$CancerOnset_Gompertz_Shape_P,
              l_params_calibrated$CancerOnset_Gompertz_Shape_D,
              l_params_calibrated$CancerOnset_Gompertz_Shape_R,
              l_params_calibrated$CancerOnset_Gompertz_Rate_P,
              l_params_calibrated$CancerOnset_Gompertz_Rate_D,
              l_params_calibrated$CancerOnset_Gompertz_Rate_R,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S1S2_P,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S1S2_D,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S1S2_R,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S2S3_P,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S2S3_D,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S2S3_R,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S3S4_P,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S3S4_D,
              l_params_calibrated$PreclinCancerProg_Exp_Rate_S3S4_R)
)  

#Create a table to display the dataframe
library(knitr)
kable(df_params_comparison, 
      caption = "Calibrated parameters for Adenoma pathway",
      col.names = c("Parameter", "Adenoma"),
      digits = 3,
      format = "html",align = "l")
}

```

## Events by lesion type

```{r echo=FALSE, message=FALSE, warning=FALSE}

#Run a natural history simulation with the best parameter set
library(simcrc)

SSP_cal <- calibration_setup$SSP_pathway #TRUE if we want to include SSP pathway

# Get base population
n_pop <- calibration_setup$n_pop

dt_pop <- get_dt_population(year = calibration_setup$cohort_year,
                            byear = calibration_setup$birth_year,
                            p_female = calibration_setup$p_female,
                            p_white = calibration_setup$p_white,
                            n_pop = calibration_setup$n_pop,
                            dt_life_table_F = calibration_setup$life_table_fem,
                            dt_life_table_M = calibration_setup$life_table_male)

# Load all initial parameters and set the calibrated parameters from previous versions
l_params_init <- calibration_setup$l_params_init

#Update the parameters with the calibrated SSP parameters
l_params_all <- simcrc::update_param_list(l_params_all = l_params_init, 
                                  params_updated = l_params_calibrated)

# Run simcrc nathist according to whether SSP pathway is included or not

SSP_cal <- calibration_setup$SSP_pathway

l_out_simcrc <- simcrc::simcr_nathist_ssp_DES(l_params_all = l_params_all, 
                                                dt_pop       = dt_pop, 
                                                SSP_pathway = SSP_cal)

nat_hist_output <- l_out_simcrc$dt_crc_pop

#get an id row for each person
nat_hist_output[, id_row := 1:.N , by = id]

#get histogram of number of adenomas per person

nat_hist_output_agg <- nat_hist_output[, .(
  n_adenomas_dev = sum(lesion_type == "Adenoma" & develop_lesion == 1),
  n_ssp_dev      = sum(lesion_type == "SSP" & develop_lesion == 1)
), by = .(id)]

nat_hist_output <- merge(nat_hist_output, nat_hist_output_agg, by = "id", all.x = TRUE)


library(ggplot2)
ggplot(nat_hist_output[id_row==1,], aes(x = n_adenomas_dev)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 bins = 30, fill = "blue", alpha = 0.7, color = "black") +
  # add histogram of number of ssp per person
  geom_histogram(aes(x = n_ssp_dev, y = ..count../sum(..count..)), 
                 bins = 30, fill = "green", alpha = 0.7, color = "black") +
  labs(title = "Histogram of Number of Adenomas per Person",
       x = "Number of Adenomas",
       y = "Frequency") +
  theme_minimal()

# add the average number of adenomas and ssp per person in the graph
avg_adenomas <- mean(nat_hist_output[id_row==1,]$n_adenomas_dev)
avg_ssp <- mean(nat_hist_output[id_row==1,]$n_ssp_dev)

ggplot(nat_hist_output[id_row==1,], aes(x = n_adenomas_dev)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 bins = 30, fill = "blue", alpha = 0.5, color = "black") +
  # add histogram of number of ssp per person
  geom_histogram(aes(x = n_ssp_dev, y = ..count../sum(..count..)), 
                 bins = 30, fill = "green", alpha = 0.5, color = "black") +
  geom_vline(xintercept = avg_adenomas, color = "red", linetype = "dashed", size = 1) +
  geom_vline(xintercept = avg_ssp, color = "orange", linetype = "dashed", size = 1) +
  annotate("text", x = avg_adenomas + 1, y = 0.4, label = paste("Avg Adenomas:", round(avg_adenomas,2)), color = "red") +
  annotate("text", x = avg_ssp + 1, y = 0.5, label = paste("Avg SSP:", round(avg_ssp,2)), color = "orange") +
  labs(title = "Histogram of Number of Adenomas and SSP per Person",
       x = "Number of Lesions",
       y = "Frequency") +
  theme_minimal()

```

### Histogram of age of lesion onset

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(nat_hist_output, aes(x = age_lesion_onset, fill = lesion_type)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 position = "dodge", bins = 30, alpha = 0.7, color = "black") +
  labs(title = "Histogram of Age of Lesion Onset by Lesion Type",
       x = "Age of Lesion Onset (years)",
       y = "Frequency") +
  theme_minimal() +
  scale_fill_manual(values = c("Adenoma" = "blue", "SSP" = "green"))

```

### Average of age of lesion onset by lesion type

```{r echo=FALSE, message=FALSE, warning=FALSE}
# show the n , average and sd of age of lesion onset for adenoma and ssp in a table
n_age_onset_adenoma <- nrow(nat_hist_output[lesion_type=="Adenoma" & develop_lesion==1,])
n_age_onset_ssp <- nrow(nat_hist_output[lesion_type=="SSP" & develop_lesion==1,])

avg_age_onset_adenoma <- mean(nat_hist_output[lesion_type=="Adenoma" & develop_lesion==1 ,]$age_lesion_onset)
avg_age_onset_ssp <- mean(nat_hist_output[lesion_type=="SSP" & develop_lesion==1,]$age_lesion_onset)

sd_age_onset_adenoma <- sd(nat_hist_output[lesion_type=="Adenoma" & develop_lesion==1,]$age_lesion_onset)
sd_age_onset_ssp <- sd(nat_hist_output[lesion_type=="SSP" & develop_lesion==1,]$age_lesion_onset)

df_age_onset <- data.frame(
  Lesion_Type = c("Adenoma", "SSP"),
  N_Lesions = c(n_age_onset_adenoma, n_age_onset_ssp),
  Average_Age_Onset = c(avg_age_onset_adenoma, avg_age_onset_ssp),
  SD_Age_Onset = c(sd_age_onset_adenoma, sd_age_onset_ssp)
)
  
  
# Create a table to display the average age of lesion onset
library(knitr)
kable(df_age_onset, 
      caption = "Average Age of Lesion Onset by Lesion Type",
      col.names = c("Lesion Type", "Number of Lesions", "Average Age of Onset (years)", "SD Age of Onset (years)"),
      digits = 2,
      format = "html", align = "l")
```
### Age to 6mm by lesion type

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(nat_hist_output[develop_lesion==1 & develop_ad_6mm==1,], aes(x = age_to_6mm, fill = lesion_type)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 position = "dodge", bins = 30, alpha = 0.7, color = "black") +
  labs(title = "Histogram of Age to 6mm by Lesion Type",
       x = "Age to 6mm (years)",
       y = "Frequency") +
  theme_minimal() +
  scale_fill_manual(values = c("Adenoma" = "blue", "SSP" = "green"))
```
### Summary table of age to 6 mm

```{r echo=FALSE, message=FALSE, warning=FALSE}

# show the n , average and sd of age to 6mm for adenoma and ssp in a table
n_age_to_6mm_adenoma <- nrow(nat_hist_output[lesion_type=="Adenoma" & develop_ad_6mm==1,])
n_age_to_6mm_ssp <- nrow(nat_hist_output[lesion_type=="SSP" & develop_ad_6mm==1,])
avg_age_to_6mm_adenoma <- mean(nat_hist_output[lesion_type=="Adenoma" & develop_ad_6mm==1 ,]$age_to_6mm)
avg_age_to_6mm_ssp <- mean(nat_hist_output[lesion_type=="SSP" & develop_ad_6mm==1,]$age_to_6mm)
sd_age_to_6mm_adenoma <- sd(nat_hist_output[lesion_type=="Adenoma" & develop_ad_6mm==1,]$age_to_6mm)
sd_age_to_6mm_ssp <- sd(nat_hist_output[lesion_type=="SSP" & develop_ad_6mm==1,]$age_to_6mm)
df_age_to_6mm <- data.frame(
  Lesion_Type = c("Adenoma", "SSP"),
  N_Lesions = c(n_age_to_6mm_adenoma, n_age_to_6mm_ssp),
  Average_Age_to_6mm = c(avg_age_to_6mm_adenoma, avg_age_to_6mm_ssp),
  SD_Age_to_6mm = c(sd_age_to_6mm_adenoma, sd_age_to_6mm_ssp)
)
# Create a table to display the average age to 6mm
library(knitr)
kable(df_age_to_6mm, 
      caption = "Average Age to 6mm by Lesion Type",
      col.names = c("Lesion Type", "Number of Lesions", "Average Age to 6mm (years)", "SD Age to 6mm (years)"),
      digits = 2,
      format = "html", align = "l")
```
### Age to 10 mm by lesion type

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(nat_hist_output[develop_lesion==1 & develop_ad_10mm==1,], aes(x = age_to_10mm, fill = lesion_type)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 position = "dodge", bins = 30, alpha = 0.7, color = "black") +
  labs(title = "Histogram of Age to 10mm by Lesion Type",
       x = "Age to 10mm (years)",
       y = "Frequency") +
  theme_minimal() +
  scale_fill_manual(values = c("Adenoma" = "blue", "SSP" = "green"))
```

### Summary table of age to 10 mm

```{r echo=FALSE, message=FALSE, warning=FALSE}

# show the n , average and sd of age to 10mm for adenoma and ssp in a table
n_age_to_10mm_adenoma <- nrow(nat_hist_output[lesion_type=="Adenoma" & develop_ad_10mm==1,])
n_age_to_10mm_ssp <- nrow(nat_hist_output[lesion_type=="SSP" & develop_ad_10mm==1,])
avg_age_to_10mm_adenoma <- mean(nat_hist_output[lesion_type=="Adenoma" & develop_ad_10mm==1 ,]$age_to_10mm)
avg_age_to_10mm_ssp <- mean(nat_hist_output[lesion_type=="SSP" & develop_ad_10mm==1,]$age_to_10mm)
sd_age_to_10mm_adenoma <- sd(nat_hist_output[lesion_type=="Adenoma" & develop_ad_10mm==1,]$age_to_10mm)
sd_age_to_10mm_ssp <- sd(nat_hist_output[lesion_type=="SSP" & develop_ad_10mm==1,]$age_to_10mm)
df_age_to_10mm <- data.frame(
  Lesion_Type = c("Adenoma", "SSP"),
  N_Lesions = c(n_age_to_10mm_adenoma, n_age_to_10mm_ssp),
  Average_Age_to_10mm = c(avg_age_to_10mm_adenoma, avg_age_to_10mm_ssp),
  SD_Age_to_10mm = c(sd_age_to_10mm_adenoma, sd_age_to_10mm_ssp)
)
# Create a table to display the average age to 10mm
library(knitr)
kable(df_age_to_10mm, 
      caption = "Average Age to 10mm by Lesion Type",
      col.names = c("Lesion Type", "Number of Lesions", "Average Age to 10mm (years)", "SD Age to 10mm (years)"),
      digits = 2,
      format = "html", align = "l")
```

### Age to CRC

```{r echo=FALSE, message=FALSE, warning=FALSE}

ggplot(nat_hist_output[develop_crc==1,], aes(x = age_crc, fill = lesion_type)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 position = "dodge", bins = 30, alpha = 0.7, color = "black") +
  labs(title = "Histogram of Age to CRC by Lesion Type",
       x = "Age to CRC (years)",
       y = "Frequency") +
  theme_minimal() +
  scale_fill_manual(values = c("Adenoma" = "blue", "SSP" = "green"))
```

### Summary table of age of CRC

```{r echo=FALSE, message=FALSE, warning=FALSE}
# show the n , average and sd of age to crc for adenoma and ssp in a table
n_age_to_crc_adenoma <- nrow(nat_hist_output[lesion_type=="Adenoma" & develop_crc==1,])
n_age_to_crc_ssp <- nrow(nat_hist_output[lesion_type=="SSP" & develop_crc==1,])
avg_age_to_crc_adenoma <- mean(nat_hist_output[lesion_type=="Adenoma" & develop_crc==1 ,]$age_crc)
avg_age_to_crc_ssp <- mean(nat_hist_output[lesion_type=="SSP" & develop_crc==1,]$age_crc)
sd_age_to_crc_adenoma <- sd(nat_hist_output[lesion_type=="Adenoma" & develop_crc==1,]$age_crc)
sd_age_to_crc_ssp <- sd(nat_hist_output[lesion_type=="SSP" & develop_crc==1,]$age_crc)
df_age_to_crc <- data.frame(
  Lesion_Type = c("Adenoma", "SSP"),
  N_Lesions = c(n_age_to_crc_adenoma, n_age_to_crc_ssp),
  Average_Age_to_CRC = c(avg_age_to_crc_adenoma, avg_age_to_crc_ssp),
  SD_Age_to_CRC = c(sd_age_to_crc_adenoma, sd_age_to_crc_ssp)
)
# Create a table to display the average age to crc
library(knitr)
kable(df_age_to_crc, 
      caption = "Average Age to CRC by Lesion Type",
      col.names = c("Lesion Type", "Number of Lesions", "Average Age to CRC (years)", "SD Age to CRC (years)"),
      digits = 2,
      format = "html", align = "l")
```
### Age of symptomatic diagnosis

```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(nat_hist_output[crc_dx_i==1,], aes(x = age_dx_symp_i, fill = lesion_type)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 position = "dodge", bins = 30, alpha = 0.7, color = "black") +
  labs(title = "Histogram of Age of Symptomatic Diagnosis by Lesion Type",
       x = "Age of Symptomatic Diagnosis (years)",
       y = "Frequency") +
  theme_minimal() +
  scale_fill_manual(values = c("Adenoma" = "blue", "SSP" = "green"))
```

### Summary table of age of symptomatic diagnosis
```{r echo=FALSE, message=FALSE, warning=FALSE}
# show the n , average and sd of age of symptomatic diagnosis for adenoma and ssp in a table
n_age_dx_symp_adenoma <- nrow(nat_hist_output[lesion_type=="Adenoma" & crc_dx_i==1,])
n_age_dx_symp_ssp <- nrow(nat_hist_output[lesion_type=="SSP" & crc_dx_i==1,])
avg_age_dx_symp_adenoma <- mean(nat_hist_output[lesion_type=="Adenoma" & crc_dx_i==1 ,]$age_dx_symp_i)
avg_age_dx_symp_ssp <- mean(nat_hist_output[lesion_type=="SSP" & crc_dx_i==1,]$age_dx_symp_i)
sd_age_dx_symp_adenoma <- sd(nat_hist_output[lesion_type=="Adenoma" & crc_dx_i==1,]$age_dx_symp_i)
sd_age_dx_symp_ssp <- sd(nat_hist_output[lesion_type=="SSP" & crc_dx_i==1,]$age_dx_symp_i)
df_age_dx_symp <- data.frame(
  Lesion_Type = c("Adenoma", "SSP"),
  N_Lesions = c(n_age_dx_symp_adenoma, n_age_dx_symp_ssp),
  Average_Age_dx_symp = c(avg_age_dx_symp_adenoma, avg_age_dx_symp_ssp),
  SD_Age_dx_symp = c(sd_age_dx_symp_adenoma, sd_age_dx_symp_ssp)
)
# Create a table to display the average age of symptomatic diagnosis
library(knitr)
kable(df_age_dx_symp, 
      caption = "Average Age of Symptomatic Diagnosis by Lesion Type",
      col.names = c("Lesion Type", "Number of Lesions", "Average Age of Symptomatic Diagnosis (years)", "SD Age of Symptomatic Diagnosis (years)"),
      digits = 2,
      format = "html", align = "l")
```
### Age of CRC death
```{r echo=FALSE, message=FALSE, warning=FALSE}
ggplot(nat_hist_output[crc_death_i==1 & death_cause=="crc",], aes(x = age_death, fill = lesion_type)) +
  geom_histogram(aes(y = ..count../sum(..count..)), 
                 position = "dodge", bins = 30, alpha = 0.7, color = "black") +
  labs(title = "Histogram of Time to CRC Death by Lesion Type",
       x = "Time to CRC Death (years)",
       y = "Frequency") +
  theme_minimal() +
  scale_fill_manual(values = c("Adenoma" = "blue", "SSP" = "green"))
```

### Summary table of age of CRC death
```{r echo=FALSE, message=FALSE, warning=FALSE}
# show the n , average and sd of age of crc death for adenoma and ssp in a table
n_age_crc_death_adenoma <- nrow(nat_hist_output[lesion_type=="Adenoma" & crc_death_i==1 & death_cause=="crc",])
n_age_crc_death_ssp <- nrow(nat_hist_output[lesion_type=="SSP" & crc_death_i==1 & death_cause=="crc",])
avg_age_crc_death_adenoma <- mean(nat_hist_output[lesion_type=="Adenoma" & crc_death_i==1 & death_cause=="crc",]$age_death)
avg_age_crc_death_ssp <- mean(nat_hist_output[lesion_type=="SSP" & crc_death_i==1 & death_cause=="crc",]$age_death)
sd_age_crc_death_adenoma <- sd(nat_hist_output[lesion_type=="Adenoma" & crc_death_i==1 & death_cause=="crc",]$age_death)
sd_age_crc_death_ssp <- sd(nat_hist_output[lesion_type=="SSP" & crc_death_i==1 & death_cause=="crc",]$age_death)
df_age_crc_death <- data.frame(
  Lesion_Type = c("Adenoma", "SSP"),
  N_Lesions = c(n_age_crc_death_adenoma, n_age_crc_death_ssp),
  Average_Age_crc_death = c(avg_age_crc_death_adenoma, avg_age_crc_death_ssp),
  SD_Age_crc_death = c(sd_age_crc_death_adenoma, sd_age_crc_death_ssp)
)
# Create a table to display the average age of crc death
library(knitr)
kable(df_age_crc_death, 
      caption = "Average Age of CRC Death by Lesion Type",
      col.names = c("Lesion Type", "Number of Lesions", "Average Age of CRC Death (years)", "SD Age of CRC Death (years)"),
      digits = 2,
      format = "html", align = "l")
```

### Summary table of events by lesion type


```{r echo=FALSE, message=FALSE, warning=FALSE}

#Keep only lesions that turn over cancer 
nat_hist_output <- nat_hist_output[crc_dx_i==1,]

#Get a summary of age of lesion onset, time_to_6mm, age_to_6mm,time_to_10mm, age_to_10mm, 
# time_to_crc, age_crc, time_to_stage2, time_to_stage3,  time_to_stage4, age_dx_symp_i, crc_death_i,time_crc_death_i by lesion type
nat_hist_output_summary <- nat_hist_output[, .(
  n_lesions = .N,
  age_onset = mean(age_lesion_onset, na.rm = TRUE),
  time_to_6mm = mean(time_to_6mm, na.rm = TRUE),
  age_to_6mm = mean(age_to_6mm, na.rm = TRUE),
  time_to_10mm = mean(time_to_10mm, na.rm = TRUE),
  age_to_10mm = mean(age_to_10mm, na.rm = TRUE),
  time_to_crc = mean(time_to_crc, na.rm = TRUE),
  age_crc = mean(age_crc, na.rm = TRUE),
  time_to_stage2 = mean(time_to_stage2, na.rm = TRUE),
  time_to_stage3 = mean(time_to_stage3, na.rm = TRUE),
  time_to_stage4 = mean(time_to_stage4, na.rm = TRUE),
  age_dx_symp_i = mean(age_dx_symp_i, na.rm = TRUE),
  crc_death_i = mean(crc_death_i, na.rm = TRUE),
  time_crc_death_i = mean(time_crc_death_i, na.rm = TRUE)
), by=lesion_type]

#Create a table to display the summary
library(knitr)
kable(nat_hist_output_summary, 
      caption = "Summary of events by lesion type",
      col.names = c("Lesion Type", "Number of lesions","Age of Onset (years)", "Time to 6mm (years)", "Age to 6mm (years)",
                    "Time to 10mm (years)", "Age to 10mm (years)", "Time to CRC (years)",
                    "Age at CRC Onset (years)", "Time to Stage 2 (years)",
                    "Time to Stage 3 (years)", "Time to Stage 4 (years)",
                    "Age at Symptomatic Diagnosis (years)", "CRC Death Age (years)",
                    "Time to CRC Death (years)"),
      digits = 2,
      format = "html", align = "l")

```


## Dwell times

```{r echo=FALSE, message=FALSE, warning=FALSE}

# Calculates adenoma dwell time

Adenoma_dwell <- mean(nat_hist_output[lesion_type=="Adenoma",]$t_Adonset_Preclin, na.rm = TRUE)

Sojourn_time  <- mean(nat_hist_output[lesion_type=="Adenoma",]$t_Preclin_Sxdet, na.rm = TRUE)

Total_dwell   <- mean(nat_hist_output[lesion_type=="Adenoma",]$t_Adonset_Sxdet, na.rm = TRUE)

# Calculate SSP dwell time
SSP_dwell <- mean(nat_hist_output[lesion_type=="SSP",]$t_Adonset_Preclin, na.rm = TRUE)
Sojourn_time_SSP  <- mean(nat_hist_output[lesion_type=="SSP",]$t_Preclin_Sxdet, na.rm = TRUE)
Total_dwell_SSP   <- mean(nat_hist_output[lesion_type=="SSP",]$t_Adonset_Sxdet, na.rm = TRUE)

# Create a data frame for the dwell times
dwell_times <- data.frame(
  Lesion_Type = c("Adenoma", "SSP"),
  Dwell_Time = c(Adenoma_dwell, SSP_dwell),
  Sojourn_Time = c(Sojourn_time, Sojourn_time_SSP),
  Total_Dwell = c(Total_dwell, Total_dwell_SSP)
)

# Create a table to display the dwell times
library(knitr)
kable(dwell_times, 
      caption = "Dwell times for Adenoma and SSP lesions",
      col.names = c("Lesion Type", "Dwell Time (years)", "Sojourn Time (years)", "Total Dwell Time (years)"),
      digits = 2,
      format = "html", align = "l")


```
